### 2020-11-30 doc/manuscript/Dow_manuscript.Rmd
results - climwin
knit in new figure, deleted old draft version,
issues #26, #34

climwin_caption <- "Figure 3. THIS IS OUT OF DATE. Landscapes of relationships between the day of year on which 25% of annual growth is achieved (DOY_25) and temperature in prior weeks for ring- and diffuse-porous trees at SCBI and Harvard Forest. Shown are matrices of linear coefficients of first-order linear regressions between temperature and DOY_25, where Window Open and Window Close indicate number of weeks prior to DOY_25 (ring-porous: DATE at SCBI, DATE at HF; diffuse-porous: DATE at SCBI, DATE at HF). Black boxes indicate the optimal window."

@@

#SI figure numbers
climwin_rp_DOY25_SCBI = "S1"
climwin_dp_DOY25_SCBI = "S2"
climwin_rp_DOY25_SCBI = "S3"
climwin_dp_DOY25_SCBI = "S4"
#SI figure captions
climwin_rp_DOY25_SCBI_short_caption <- "Figure S1. Full climwin output for DOY 25 for ring porous species at SCBI."
climwin_dp_DOY25_SCBI_short_caption <- "Figure S2. Full climwin output for DOY 25 for diffuse porous species at SCBI."
climwin_rp_DOY25_HARV_short_caption <- "Figure S3. Full climwin output for DOY 25 for ring porous species at Harvard Forest."
climwin_dp_DOY25_HARV_short_caption <- "Figure S4. Full climwin output for DOY 25 for diffuse porous species at Harvard Forest."

@@

For the majority of weekly time windows from Jan. 1 to $DOY_{25}$, there was negative relationship between temperature and $DOY_{25}$, meaning that warmer temperatures shifted growth earlier in the season (Figs. `r climwin`, `r climwin_rp_DOY25_SCBI`, `r climwin_dp_DOY25_SCBI`). 
This held true for both ring- and diffuse-porous trees at both sites, *albeit* with stronger relationships for diffuse-porous trees. 
*(Describe the landscape:)*
In general, there were significant negative relationships between temperature and $DOY_{25}$ for any time period beginning $\ge$ **5** weeks prior to $DOY_{25}$, ending  $\le$ **8-20** weeks prior depending on wood-type and site, and covering at least a **3**-week period. 
Relationships tended to be weaker and more stochastic in sign for short time periods, particularly those just prior to $DOY_{25}$.

Optimal windows occurred from **3/22-5/7** for ring-porous species and from **2/19-5/21** for diffuse-porous species.

```{r climwin, out.width="100%", echo=FALSE, fig.align="center", fig.cap= climwin_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/climwin.png")
```

>>>>

climwin_caption <- "Figure 3. Landscapes of relationships between the day of year on which 25% of annual growth is achieved (DOY_25) and temperature in prior weeks for ring- (1ST ROW) and diffuse-porous (2ND ROW) trees at SCBI (FIRST COLUMN) and Harvard Forest (SECOND COLUMN). Shown are matrices of linear coefficients of first-order linear regressions between temperature and DOY_25, where Window Open and Window Close indicate number of weeks prior to DOY_25 (ring-porous: May 4 at SCBI, May 15 at HF; diffuse-porous: June 4 at SCBI, June 14 at HF). Black boxes indicate the optimal window (ring-porous:  March 22- April 9 at SCBI, April 2 - May 07 at HF; diffuse-porous: Feb. 19- May 21 at SCBI, March 19 - May 07 at HF)."

@@

#SI figure numbers
all_climwin_SI_figs = " S1-S4"
climwin_rp_DOY25_SCBI = "S1"
climwin_dp_DOY25_SCBI = "S2"
climwin_rp_DOY25_SCBI = "S3"
climwin_dp_DOY25_SCBI = "S4"
#SI figure captions
climwin_rp_DOY25_SCBI_short_caption <- "Figure S1. Full climwin output for DOY 25 for ring porous species at SCBI."
climwin_dp_DOY25_SCBI_short_caption <- "Figure S2. Full climwin output for DOY 25 for diffuse porous species at SCBI."
climwin_rp_DOY25_HARV_short_caption <- "Figure S3. Full climwin output for DOY 25 for ring porous species at Harvard Forest."
climwin_dp_DOY25_HARV_short_caption <- "Figure S4. Full climwin output for DOY 25 for diffuse porous species at Harvard Forest."

@@

For the majority of weekly time windows from Jan. 1 to $DOY_{25}$, there was neutral negative relationship between temperature and $DOY_{25}$, meaning that warmer temperatures shifted growth earlier in the season (Figs. `r climwin`, `r all_climwin_SI_figs`). 
This held true for both ring- and diffuse-porous trees at both sites. 
The strongest relationships, including but not limited to the optimal time windows (Table `r mean_growth_parameters_table`), occurred for time windows closing $\le$ 5 weeks prior to $DOY_{25}$. 
(In general, there were significant negative relationships between temperature and $DOY_{25}$ for any time period beginning $\ge$ **5** weeks prior to $DOY_{25}$, ending  $\le$ **8-20** weeks prior depending on wood-type and site, and covering at least a **3**-week period (`r all_climwin_SI_figs`).
Relationships tended to be weaker and more stochastic in sign for short time periods, particularly those just prior to $DOY_{25}$.)
(**Cameron, I'm not sure if the above text is up-to-date... Also, see [issue 34](https://github.com/EcoClimLab/growth_phenology/issues/34)** )

```{r climwin, out.width="100%", echo=FALSE, fig.align="center", fig.cap= climwin_caption}
# Created in RScripts/additional_figures.R
knitr::include_graphics("tables_figures/climwin_figure.png")
```
